Verifying Demonstrations

### 2017-12-14 paper/intro.tex
Removes files into separate directories
Adds Makefile and adapts files for paper
Adds slides, distance bounding still to do

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{fig/Jacobs-method.jpg}
  \end{figure}
\end{frame}

@@

Voting has three requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{itemize}
  \item Eligibility: anyone can verify that each vote cast is legitimate.
  \item Universal verifiability: anyone can verify that the result is according 
    to the cast votes.
  \item Individual verifiability: every voter can verify that their vote is 
    included in the result.
\end{itemize}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verification}.

@@

\subsection{Contributions}

>>>>

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{Jacobs-method.jpg}
  \end{figure}
\end{frame}

@@

Voting has three requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{frame}
\begin{description}
  \item[Eligibility] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability] every voter can verify that their vote is 
    included in the result.
\end{description}
\end{frame}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verifiability}.

\mode<presentation>{%
\begin{frame}
  \begin{description}
    \item[Privacy] no increased risk to participants.
  \end{description}
\end{frame}
}

@@

\mode<article>{%
\subsection{Contributions}
}
